Taking Dyads Seriously

### 2018-02-22 paper/4_app.tex
reorg by mdw, tiny changes

\begin{figure}
	\centering   
	\begin{tabular}{cc}
		\multicolumn{2}{l}{\textbf{Reiter \& Stam (2003)}} \\
		\includegraphics[width=.4\textwidth]{reiter_stam_roc_outSample.pdf} & 
		\includegraphics[width=.4\textwidth]{reiter_stam_pr_outSample.pdf} \\
		\multicolumn{2}{l}{\textbf{Weeks (2012)}} \\
		\includegraphics[width=.4\textwidth]{weeks_roc_outSample.pdf} & 
		\includegraphics[width=.4\textwidth]{weeks_pr_outSample.pdf} \\
		\multicolumn{2}{l}{\textbf{Gibler (2017)}} \\
		\includegraphics[width=.4\textwidth]{gibler_roc_outSample.pdf} & 
		\includegraphics[width=.4\textwidth]{gibler_pr_outSample.pdf} \\
	\end{tabular}
	\caption{Assessments of out-of-sample predictive performance for Gibler (2017) using ROC curves, PR curves, and separation plots.}
	\label{fig:perf}	
\end{figure}

>>>>

\begin{figure}
	\centering   
	\begin{tabular}{cc}
		\multicolumn{2}{l}{\textbf{Reiter \& Stam (2003)}} \\
		\includegraphics[width=.4\textwidth]{graphics/reiter_stam_roc_outSample.pdf} & 
		\includegraphics[width=.4\textwidth]{graphics/reiter_stam_pr_outSample.pdf} \\
		\multicolumn{2}{l}{\textbf{Weeks (2012)}} \\
		\includegraphics[width=.4\textwidth]{graphics/weeks_roc_outSample.pdf} & 
		\includegraphics[width=.4\textwidth]{graphics/weeks_pr_outSample.pdf} \\
		\multicolumn{2}{l}{\textbf{Gibler (2017)}} \\
		\includegraphics[width=.4\textwidth]{graphics/gibler_roc_outSample.pdf} & 
		\includegraphics[width=.4\textwidth]{graphics/gibler_pr_outSample.pdf} \\
	\end{tabular}
	\caption{Assessments of out-of-sample predictive performance for Gibler (2017) using ROC curves, PR curves, and separation plots.}
	\label{fig:perf}	
\end{figure}
